%% cv.tex
%% Copyright 2017 Zeyi Fan
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
% This work has the LPPL maintenance status `maintained'.
%
% The Current Maintainer of this work is Zeyi Fan.
%
% This work consists of only the file cv.tex

\documentclass{article}
\usepackage[top=.4in, bottom=.0in, left=3in, right=0.4in,marginparwidth=2.5in]{geometry}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[absolute,overlay]{textpos}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{pstricks}
\usepackage{amssymb}
\usepackage{paralist}

\usepackage[pdfauthor={Christoph Sonntag},
            pdftitle={Christoph Sonntag's Resume},
            pdfkeywords={Machine Learning, Autoencoders, Latent Space, Artificial Intelligence, Data Mining, Web Development, Software Engineer, Music, Guitar}]{hyperref}
\usepackage{hyperref}

\definecolor{mygray}{gray}{0.95}
\definecolor{lightdark}{gray}{0.55}
\definecolor{dark}{gray}{0.3}
\definecolor{skillbg}{gray}{0.7}
\definecolor{headgreen}{RGB}{48, 227, 129}
\definecolor{headred}{RGB}{235, 44, 55}

\newcommand{\amount}{5.7in}
\setcounter{section}{-1}

\linespread{1.2}
\pagenumbering{gobble}
\renewcommand{\labelitemi}{$\blacksquare$}
\renewenvironment{itemize}[1]{\begin{compactitem}#1}{\end{compactitem}}

% Helpers

\newcommand\twodigits[1]{%
   \ifnum#1<10 0#1\else #1\fi
}

%\newcommand\hl[1]{{\ralewaysb #1}}
\newcommand\hl[1]{#1}


% Fonts

\newfontfamily\raleway{Raleway-v4020 Regular}
\newfontfamily\ralewaym{Raleway-v4020 Medium}
\newfontfamily\ralewaysb{Raleway-v4020 SemiBold}
\newfontfamily\ralewayb{Raleway-v4020 Bold}
\newfontfamily\ralewayeb{Raleway-v4020 ExtraBold}
\newfontfamily\ralewaybb{Raleway-v4020 Black}

\setmainfont{Raleway-v4020 Regular}


% Styles
\newcommand{\name}[2]{
    \begin{center}
        \Huge{
            \textcolor{dark}{\ralewayeb{#1 #2}}
        }
    \end{center}
}

\newcommand{\tagline}[1]{
    \begin{center}
        \large{
            \color{dark}
            \ralewaysb{#1}
        }
        \vspace{.2em}
    \end{center}
}

\renewcommand{\thesection}{\twodigits{\arabic{section}}.}

\titleformat{\section}
[hang]
{\ralewaysb\large\color{dark}}
{}
{.0em}
{}
[{\titlerule[0.8pt]}]

\titlespacing*{\section}{0pt}{4pt}{10pt}

\setlength{\TPHorizModule}{1mm}
\setlength{\TPVertModule}{1mm}
\setlength{\parindent}{0mm}

\newcommand{\contactline}[2]{
    \ralewaysb{#1} & \raleway{#2}
}

\newcommand{\skill}[2]{
    \vspace{.2em}
    \ralewayb{#1}

    \psset{xunit=0.197\linewidth, yunit=5pt}
    \begin{pspicture}[showgrid=false](5,1)
        \psline[linecolor=skillbg](0,0.5)(5,0.5)
        \psline[linecolor=skillbg,arrows=|-|](1,0.5)(2,0.5)
        \psline[linecolor=skillbg,arrows=|-|](3,0.5)(4,0.5)
        \psline[linecolor=skillbg,arrows=-|](0,0.5)(5,0.5)

        \psline[linecolor=black,arrows=|-|](0,0.5)(#2,0.5)
    \end{pspicture}
}

\newcommand{\block}[3]{
    {\large\ralewayb #1}

    \ralewaym{\color{lightdark}#2}
    \vspace{.3em}

    \raleway{#3}
}

\begin{document}

% background

\begin{tikzpicture}[remember picture,overlay]
  \fill[mygray] (current page.south west) rectangle ([xshift=-\amount]current page.north east);
\end{tikzpicture}

% Side Bar

\begin{textblock}{58.5}(6,7.7)
    \name{Christoph}{Sonntag}

    %\tagline{Student \& Developer}

    \section{About me}

    \color{dark}

    I started a company at sixteen, doing contract-based web development\\projects which eventually led me to pursue a degree in Internet Computing. During my studies, my interests shifted more towards 
    data science and deep learning, which was luckily also possible to follow up by choosing several courses offered by my university. I'm now a graduate student in Computer Science with a focus on data science 
    topics and interested in making machine learning models, that are more often used in crucial decision making processes with significant societal impact, more explainable and interpretable.

    \vspace{.9em}

    \section{Contact}

    \renewcommand{\arraystretch}{1.1}

    \begin{tabular}{rl}
        \contactline{Phone}{(+49) 151 70097024} \\
        \contactline{Email}{cv@snn.tg} \\
        \contactline{Website}{\href{https://snn.tg}{https://christoph.snn.tg}} \\
        \contactline{GitHub}{\href{https://github.com/chrisonntag}{@chrisonntag}} \\
        \contactline{LinkedIn}{\href{https://linkedin.com/in/christophsonntag}{/in/christophsonntag}}
    \end{tabular}

    \vspace{.9em}

    \section{Skills \& Tools}

    \skill{Python}{4}

    \skill{Java}{3}

    \skill{JavaScript}{3}

    \skill{C/C++}{2.25}

    \skill{Git}{3.5}

    \skill{Unix}{3.25}

    \skill{HTML/CSS/PHP}{4.25}

    \skill{Vim/JetBrain IDEs}{3.5}

\end{textblock}

% Main

\vspace{-25pt}  % Change this value to adjust the position of the right
\section{Education}

\block{University of Vienna, Austria}
{M.Sc. Computer Science, Major Data Science | Expected 2023}
{
    Current research interests, which I am pursuing in universtiy projects at the Research Group Visualization and Data Analysis, include Explainable and Interpretable Machine Learning Models and the structure of Latent Spaces based on Variational Autoencoders.
}

\vspace{.5em}

\block{University of Passau, Germany}
{B.Sc. Internet Computing, GPA: 2.3 | 2020}
{
    "Performance of Residual Networks on a Multi-Label Classification Problem", 1.7\\
    My thesis presents a solution to vanishing gradients and the degradation problem proposed by He et. al. by introducing shortcut connections between layers and evaluates the performance on an autonomous driving dataset.
}

\vspace{.9em}

\section{Work Experience}

\block{Software Engineer, Full-Stack Developer}
{On-contract, Germany (remote, part-time) | June 2013 - }
{
    \begin{itemize}[-]
        \item Communication, engineering and development of contract-based projects.
        \item Static and dynamic web development with PHP, node.js 
        \item Data Mining and Warehousing, automating processes in energy billing with Python and Django (\href{https://mmetering.chrisonntag.com/}{MMetering})
    \end{itemize}
}

\vspace{.5em}

\block{Lecturer}
{ZKK, University of Passau, Germany | October 2017 - July 2018 }
{
    \begin{itemize}[-]
        \item Several weekend courses for students with a non-computer-science background
        \item Introducing students to programming with Python
        \item Responsible for course planning and teaching of classes (approx. fifteen people per class, 4.47 average score on a scale from 1-5, worst to best)
    \end{itemize}
}

\vspace{.9em}

%\section{Projects}

%\block{MMetering}{}{
%    Production-running solution for recording and evaluating electricity meter-data in single- and apartment houses.
%    Django application running in a Docker environment using Redis as a message broker for scheduling requests to connected meter on a bus using the MODBUS protocol.
%    \begin{itemize}[-]
%        \item Concept, Development and Deployment on production machines
%        \item Helped me progress a lot in the following areas:
%            \begin{itemize}[-]
%                \item Communication Skills
%                \item Software Engineering
%                \item Support and continuous integration
%            \end{itemize}
%    \end{itemize}
%}

%\vspace{.9em}

\section{Volunteer Experience}

\ralewaysb Stundent Council Member, \raleway University of Passau \hfill 04/2016 - 10/2020
\begin{itemize}[-]
  \item Support students on administrative issues and as a mentor, 
  \item Student representative on several professors appeal committees, 
  \item Main leading role of a team of 12 organizers managing over 100 volunteers in a campus-wide event with a revenue of more than 20k Euro 
\end{itemize}

\ralewaysb Fire Department, \raleway Active Member \hfill 09/2012 - 
\begin{itemize}[-]
  \item Technical assistance and help after car accidents (special training).
  \item Training badge for fire fighting.
  \item Special education workshop for carrying respiratory protective equipment.
\end{itemize}


\vspace{.9em}
\section{Other Interests}
Music (listening as well as playing the guitar or messing around with Logic Pro); Skiing; taking part in Hackathons; Politics; Clever Automations; Art History; Applied Arts and Design; coffee making

\vspace{.9em}
\section{What I'm looking for}
I'm looking for exciting, challenging tasks and people that really love what they do. Although I enjoy programming and researching on specific tasks and topics, I also like taking part in a project's organization in order to grasp the big picture. 

\end{document}

